---
title: "Programming for Data Science (Bank Data)"
author: "Gasha Sarwono"
date: "3/21/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango

---

## 1.Explanataion
##### Hello my name is Gasha Sarwono Putra and this is my Rmd.

##### In this Rmd i want to exploratory data analysis using data bank.

##### I hope you enjoy it :)

## 2.Import Data
**Import data bank to RStudio**
```{r}
bank <- read.csv("bank-additional/bank-additional-full.csv", sep=";")
```

### 2.1 Activated library
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
```

## 3.Data Inspection
**Inspect data before analysis data**
```{r}
#see 6 first data
head(bank)
```

```{r}
##see 6 last data
tail(bank)
```

```{r}
#see total row and column
dim(bank)
```

```{r}
#see index name of column
names(bank)
```
**Summary Data Inspection:**

1. Data bank has 41188 rows and 21 columns

2. Names from index column: 
"age","job","marital","education","default","housing","loan","contact","month","day_of_week","duration","campaign","pdays","previous","poutcome","emp.var.rate",cons.price.idx","cons.conf.idx","euribor3m","nr.employed","y"


## 4.Data Cleansing
**Before cleansing the data, you need to know the point of each column, here is the explanation:**

**1. Bank client data:**

- age : customer age (numeric)
- job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
- marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
- education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
- default: has credit in default? (categorical: 'no','yes','unknown')
- housing: has housing loan? (categorical: 'no','yes','unknown')
- loan: has personal loan? (categorical: 'no','yes','unknown')

**2. Related with the last contact of the current campaign:**

- contact: contact communication type (categorical: 'cellular','telephone')
- month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')
- day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')
- duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.

**3. Other attributes:**

- campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
- pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
- previous: number of contacts performed before this campaign and for this client (numeric)
- poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')

**4. Social and economic context attributes**

- emp.var.rate: employment variation rate - quarterly indicator (numeric)
- cons.price.idx: consumer price index - monthly indicator (numeric)
- cons.conf.idx: consumer confidence index - monthly indicator (numeric)
- euribor3m: euribor 3 month rate - daily indicator (numeric)
- nr.employed: number of employees - quarterly indicator (numeric)

**5. Output variable (desired target):**

- y - has the client subscribed a term deposit? (binary: 'yes','no')*
```{r}
#check data type for each column
str(bank)
```
**There is a column with an inappropriate data type:**
**( "job", "maritial", "education", "default", "housing", "loan", "contact", "month", "day_of_week","poutcome", "y" )**

```{r}
#change type data with an inappropiate
bank$job <- as.factor(bank$job)
bank$marital <- as.factor(bank$marital)
bank$education <- as.factor(bank$education)
bank$default <- as.factor(bank$default)
bank$housing <- as.factor(bank$housing)
bank$loan <- as.factor(bank$loan)
bank$contact <- as.factor(bank$contact)
bank$month <- as.factor(bank$month)
bank$day_of_week <- as.factor(bank$day_of_week)
bank$poutcome <- as.factor(bank$poutcome)
bank$y <- as.factor(bank$y)
```

```{r}
#check type data after changing
str(bank)
```

**Type data for all columns is already appropriate**

```{r}
#check missing value
colSums(is.na(bank))
```
**Data bank no have missing value**

## Summary
##### 1. Data bank has 41188 rows and 21 columns
##### 2. Names from index column: 
##### "age","job","marital","education","default","housing","loan","contact","month","day_of_week","duration","campaign","pdays","previous","poutcome","emp.var.rate",cons.price.idx","cons.conf.idx","euribor3m","nr.employed","y"
##### 3. Type data for bank data consist of interger, factor, and numeric
##### 4. Data bank no have missing value
